---
title: "SHMIM CFA"
format: html
editor: visual
---

# SHMIM CFA Study 2 (1B in the manuscript)

## Load Packages

```{r}
library(lavaan)
```

## Read Data

```{r}
library(readxl)

shmimdata <- read_excel("shmimdata.xlsx")
```

## Base Model Specification

```{r}
shmim <- 'phys_reaction  =~ SHMIM_1 + SHMIM_2 + SHMIM_3 
                cog_distress =~ SHMIM_4 + SHMIM_5 + SHMIM_6
                vividness =~ SHMIM_7 + SHMIM_8 + SHMIM_9
                intentionality =~ SHMIM_10 + SHMIM_11 + SHMIM_12
                per_control =~ SHMIM_13 + SHMIM_14 + SHMIM_15'
```

### Fitting Model to Data

```{r}
shmim_model <- cfa(shmim, data = shmimdata, estimator= "MLR", std.lv=TRUE)
```

### Data Summary

```{r}
summary(shmim_model, fit.measures = TRUE, standardized=TRUE, rsquare=TRUE)
```

### Configural Invariance (Fan/Non-Fan)

```{r}
fit<-cfa(shmim,
         data = shmimdata,
         group = "horrorfan",
         std.lv = TRUE)  

summary(fit,
        fit.measures = TRUE, 
        standardized = TRUE,
        rsquare = TRUE)
```

### Loadings Model (Fan/Non-Fan)

```{r}
fit<-cfa(shmim,
         data = shmimdata,          
         group = "horrorfan",          
         group.equal = c("loadings"),
         std.lv=TRUE)  

summary(fit, 
        fit.measures = TRUE,
        standardized = TRUE,
        rsquare = TRUE)
```

### Intercepts Model (Fan/Non-Fan)

```{r}
fit<-cfa(shmim,
         data = shmimdata,
         group = "horrorfan",
         group.equal = c("loadings", 
                         "intercepts"),
         std.lv=TRUE)

summary(fit,         
        fit.measures = TRUE,
        standardized = TRUE,
        rsquare = TRUE)
```

### Measurement Invariance Summary (Fan/Non-Fan)

```{r}
config.model <-cfa(shmim, data = shmimdata, group = "horrorfan", std.lv=TRUE)
load.model <-cfa(shmim, data = shmimdata, group = "horrorfan", group.equal = c("loadings"), std.lv=TRUE) 
int.model  <-cfa(shmim, data = shmimdata, group = "horrorfan", group.equal = c("intercepts", "loadings"), std.lv=TRUE)

fitMeasures(config.model, c("cfi","rmsea","srmr","aic","bic")) 
fitMeasures(load.model, c("cfi","rmsea","srmr","aic","bic")) 
fitMeasures(int.model, c("cfi","rmsea","srmr","aic","bic")) 
```

# Dystopia CFA

## Read Data

```{r}
library(readxl)

dystopia <- read_excel("dystopia.xlsx")

dystopia[dystopia == -99] <- NA 
```

## Base Model Specification

```{r}
shmim <- 'phys_reaction  =~ SHMIM_1 + SHMIM_2 + SHMIM_3 
                cog_distress =~ SHMIM_4 + SHMIM_5 + SHMIM_6
                vividness =~ SHMIM_7 + SHMIM_8 + SHMIM_9
                intentionality =~ SHMIM_10 + SHMIM_11 + SHMIM_12
                per_control =~ SHMIM_13 + SHMIM_14 + SHMIM_15'
```

### Fitting Model to Data

```{r}
dystopia_model <- cfa(shmim, data = dystopia, estimator= "MLR", std.lv=TRUE)
```

### Data Summary

```{r}
summary(dystopia_model, fit.measures = TRUE, standardized=TRUE, rsquare=TRUE)
```

## Dystopia Reliabilities (Omegas)

```{r}
library(semTools)

compRelSEM(dystopia_model)
```

```{r}
semTools::compRelSEM(
  dystopia_model,
  return.total = TRUE
)
```

## Dystopia Reliabilities (Alphas)

```{r}
library(psych)

# Physiological Reaction
alpha_phys <- psych::alpha(
  dystopia[, c("SHMIM_1", "SHMIM_2", "SHMIM_3")]
)$total$raw_alpha

# Cognitive Distress
alpha_cog <- psych::alpha(
  dystopia[, c("SHMIM_4", "SHMIM_5", "SHMIM_6")]
)$total$raw_alpha

# Vividness
alpha_vivid <- psych::alpha(
  dystopia[, c("SHMIM_7", "SHMIM_8", "SHMIM_9")]
)$total$raw_alpha

# Intentionality
alpha_intent <- psych::alpha(
  dystopia[, c("SHMIM_10", "SHMIM_11", "SHMIM_12")]
)$total$raw_alpha

# Perceived Control
alpha_control <- psych::alpha(
  dystopia[, c("SHMIM_13", "SHMIM_14", "SHMIM_15")]
)$total$raw_alpha

# Display all alpha estimates
round(c(
  phys_reaction = alpha_phys,
  cog_distress = alpha_cog,
  vividness = alpha_vivid,
  intentionality = alpha_intent,
  per_control = alpha_control
), 3)

```

```{r}
alpha_total <- psych::alpha(
  dystopia[, paste0("SHMIM_", 1:15)]
)

alpha_total$total$raw_alpha
```

# Language Invariance

Combined data from Study 2(1B) and Dystopia

## Load Packages

```{r}
library(lavaan)
```

## Read Data

```{r}
library(readxl)

langdata <- read_excel("language_invariance.xlsx")

langdata[langdata == -99] <- NA 
```

## Base Model Specification

```{r}
shmim <- 'phys_reaction  =~ SHMIM_1 + SHMIM_2 + SHMIM_3 
                cog_distress =~ SHMIM_4 + SHMIM_5 + SHMIM_6
                vividness =~ SHMIM_7 + SHMIM_8 + SHMIM_9
                intentionality =~ SHMIM_10 + SHMIM_11 + SHMIM_12
                per_control =~ SHMIM_13 + SHMIM_14 + SHMIM_15'
```

### Fitting Model to Data

```{r}
language_model <- cfa(shmim, data = langdata, estimator= "MLR", std.lv=TRUE)
```

### Data Summary

```{r}
summary(language_model, fit.measures = TRUE, standardized=TRUE, rsquare=TRUE)
```

## Configural Invariance

```{r}
fit<-cfa(shmim,
         data = langdata,
         group = "language",
         std.lv = TRUE)  

summary(fit,
        fit.measures = TRUE, 
        standardized = TRUE,
        rsquare = TRUE)
```

## Loadings Model

```{r}
fit<-cfa(shmim,
         data = langdata,          
         group = "language",          
         group.equal = c("loadings"),
         std.lv=TRUE)  

summary(fit, 
        fit.measures = TRUE,
        standardized = TRUE,
        rsquare = TRUE)
```

## Intercepts Model

```{r}
fit<-cfa(shmim,
         data = langdata,
         group = "language",
         group.equal = c("loadings", 
                         "intercepts"),
         std.lv=TRUE)

summary(fit,         
        fit.measures = TRUE,
        standardized = TRUE,
        rsquare = TRUE)
```

## Measurement Invariance Summary

```{r}
config.model <-cfa(shmim, data = langdata, group = "language", std.lv=TRUE)
load.model <-cfa(shmim, data = langdata, group = "language", group.equal = c("loadings"), std.lv=TRUE) 
int.model  <-cfa(shmim, data = langdata, group = "language", group.equal = c("intercepts", "loadings"), std.lv=TRUE)

fitMeasures(config.model, c("cfi","rmsea","srmr","aic","bic")) 
fitMeasures(load.model, c("cfi","rmsea","srmr","aic","bic")) 
fitMeasures(int.model, c("cfi","rmsea","srmr","aic","bic")) 
```
